(working title) Local Physiological Adaptation in \textit{Mimulus cardinalis}

### 2015-04-27 ms/ms.Rnw
Worked on ms

<<focClim, echo = FALSE>>=
# Read in climate data for 16 focal populations to use in making Table 1
# need to make this available from ms directory
load('~/Google Drive/CardLocalAdaptation/Data/Climate/Robjects/focClim.RData') # focClim

@@

\subsubsection*{Water}

For watering treatments, we simulated two extreme types of streams where \textit{M. cardinalis} grows. In the well-watered treatment, we simulated a large stream with that never goes dry during the summer growing season. In the drought treatment, we simulated a small stream that has ample flow at the beginning of the season, but gradually dries down as the winter snow pack melts. In both treatments, plants were bottom-watered using with water from chilled by MAKE AND MODEL OF CHILLER to 7.5 degrees??? Check temp! MARKER - continue here!!!        Before May 20 (36 days): 7.5 min (complete flood) every 2 hours
      between May 20 to June 10 (57 days), down to 30 seconds, 1x per day
			Wet: daily/constant irrigation with cooled water
			Dry: start at week \#, gradually decrease watering frequency/level

@@

\subsection*{Measurements: Growth and photosynthesis}

\begin{table}[ht]
   \centering
   \topcaption{Traits}
   \begin{tabular}{@{} ll @{}}
      \toprule
  Trait & Units \\
      \midrule
  Day of germination  & day \\
  Leaf expansion rate  &  mm day$^{-1}$  \\
  Shoot elongation rate  &  mm or cm day$^{-1}$  \\
  Harvest dry mass &  g  \\
  Photosynthetic rate &  $\mu$mol CO$_2$ m$^{-2}$ s$^{-1}$\\
  Mortality &  Probability?  \\
	    \bottomrule
   \end{tabular}
\end{table}

@@

\cdm{which traits: germination, growth rate, biomass, biomass allometry, leaf traits, photosynthesis?, mortality?}
We tested for Population, Treatment, and Population $\times$ Treatment interactions using mixed model ANOVA with Family included as a random factor. Models were fit by restricted maximum likelihood using lmer from the R package \pkg{lme4} \citep{Bates_etal_2014}. Significant fixed effect terms were selected using a step-wise backward elimination procedure implemented with the step function in the R package \pkg{lmerTest} version 2.0-11 \citep{Kuznetsova_etal_2014}. Denominator degrees of freedom for $F$-tests were estimated using Satterthwaite's approximation. Significant Population effect indicate intrinsic trait differences; significant Population $\times$ Treatment effects indicate population differences in plasticity. For growth rate, we also accounted for differences in germination rate by including day of germination as a factor.

\subsection*{Principal components of germination, growth, and photosynthesis}

<<Principal Components>>=

@@

>>>>

<<focClim, echo = FALSE>>=
# Read in climate data for 16 focal populations to use in making Table 1
# [MAYBE SHOULD RENAMED "ExtendedTable1" or something?]
load(paste(pathDat, "/focClim.RData", sep = ""))

@@

\subsubsection*{Watering treatments}

For watering treatments, we simulated two extreme types of streams where \textit{M. cardinalis} grows. In the well-watered treatment, we simulated a large stream that never goes dry during the summer growing season. In the drought treatment, we simulated a small stream that has ample flow at the beginning of the season, but gradually dries down as the winter snow pack melts. In both treatments, plants were bottom-watered using  water chilled to 7.5 [check] by MAKE AND MODEL OF CHILLER. Plants in the well-watered treatment were fully saturated every two hours during the day. Watering in the drought treatment gradually declined from every two hours to every day between May 20 (36 days after sowing) and 10 June (57 days after sowing). Simultaneously, the amount of bottom-watering per flood decreased, such that only the bottom of the cone-tainers were wetted by the end of the experiment.

@@

\subsection*{Growth and photosynthesis}

\begin{table}[ht]
   \centering
   \topcaption{Traits}
   \begin{tabular}{@{} ll @{}}
      \toprule
  Trait & Units \\
      \midrule
  Day of germination  & day \\
  Leaf expansion rate  &  mm day$^{-1}$  \\
  Shoot elongation rate  &  mm or cm day$^{-1}$  \\
  Harvest dry mass &  g  \\
  Photosynthetic rate &  $\mu$mol CO$_2$ m$^{-2}$ s$^{-1}$\\
  Mortality &  Probability?  \\
	    \bottomrule
   \end{tabular}
   \label{table:Table_traits}
\end{table}

@@

For all traits (Table~\ref{table:Table_traits}) we tested for Population, Treatment, and Population $\times$ Treatment interactions. We interpreted significant Population effects to indicate intrinsic variation and Population by Treatment effects to indicate variation in plasticity. As mentioned above, we survival and GLM models for germination rate and mortality, respectively. For all other traits, we used mixed model ANOVAs with Family included as a random factor. Models were fit by restricted maximum likelihood using lmer from the R package \pkg{lme4} \citep{Bates_etal_2014}. Significant fixed effect terms were selected using a step-wise backward elimination procedure implemented with the step function in the R package \pkg{lmerTest} version 2.0-11 \citep{Kuznetsova_etal_2014}. Denominator degrees of freedom for $F$-tests were estimated using Satterthwaite's approximation. Significant Population effect indicate intrinsic trait differences; significant Population $\times$ Treatment effects indicate population differences in plasticity. For growth rate, we also accounted for differences in germination rate by including day of germination as a factor.

\subsection*{Principal components of germination, growth, and photosynthesis}
[maybe this goes in Results?]
We summarized population-level coefficients, after factoring out Treatment and other effects, using principal components. Spec
<<Principal Components>>=

@@

MARKER - continue here!!!
